---
title: "hw6"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(modelr)
set.seed(1)
```

Problem 1
```{r}
bw_data=read.csv("birthweight.csv") %>% 
  mutate(
    babysex=recode(babysex, "1"="male", "2"="female"),
    frace=recode(frace, "1"="white", "2"="black", "3"="asian", "4"="puerto_rican", "8"="other", "9"="unknown"),
    malform=recode(malform, "0"="absent", "1"="present"),
    mrace=recode(mrace, "1"="white", "2"="black", "3"="asian", "4"="puerto_rican", "8"="other")
  )
colSums(is.na(bw_data)) 
# no missing data
```

```{r}
lm0_test = lm(bwt ~ ., data = bw_data)
step(lm0_test, direction = 'backward')
# using stepwise regression to choose model, and the model I choose including predictors: babysex, baby' s head circumference, baby's length and so on.
lm0 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = bw_data)
summary(lm0)

bw_data %>% 
  add_predictions(model = lm0, var = "predict") %>% 
  add_residuals(model = lm0, var = "residual") %>%
  ggplot(aes(x = predict, y = residual)) + 
  geom_point(alpha = 0.2) +
  geom_smooth(color = "yellow") + 
  labs(title = "Model residuals against fitted values", 
       y = "Residuals",
       x = "Fitted Values"
       )
```

```{r}
cv_df=bw_data %>% 
  crossv_mc(100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    lm0=map(.x=train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data=.x)),
    lm1=map(.x=train, ~lm(bwt~blength+gaweeks, data=.x)),
    lm2=map(.x=train, ~lm(bwt~bhead + blength + babysex + bhead*blength+ blength*babysex + bhead*blength*babysex, data =.x)),
    rmse_lm0= map2_dbl(.x=lm0, .y=test, ~rmse(.x, .y)),
    rmse_lm1=map2_dbl(.x=lm1, .y=test, ~rmse(.x, .y)),
    rmse_lm2=map2_dbl(.x=lm2, .y=test, ~rmse(.x, .y))
  )

cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

From the figure we can see that the model that we fit has the lowest rmse, there’s clearly some improvement in predictive accuracy. The model with interacion performs worse than `lm0`, but still better than the model with only two predictors which does not take full advantage of the data.

Problem 2
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_mod= weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    reslt_g = map(models, broom::glance),
    reslt_t = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest() %>% 
  group_by(.id) %>%
  summarise(r_squared = unique(r.squared),
            log_beta = log(prod(estimate)))
```

```{r}
weather_mod %>% 
  ggplot(aes(x=r_squared))+
  geom_density()+
  labs(title = "Distribution of r-squared")
weather_mod %>% 
  ggplot(aes(x=log_beta))+
  geom_density()+
  labs(title="Distribution of log(beta0*beta1)")
```

Distribution of r_squared is nearly normally distributed, but a bit right skewed, might because of some outliers in the sample. 

Distribution of log(beta0*beta1) is pretty much the same way.
```{r}
quantile(weather_mod$r_squared, c(0.025, 0.975))
quantile(weather_mod$log_beta, c(0.025, 0.975))
```

